Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-06-23 prop_letter.tex
prop_letter.tex and "Kochen-Specker Theorem in QIVPM.pptx" Updating...

\begin{definition}\label{def:delta-deterministic}An QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
is called $\delta$-deterministic if either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$ for
any $P\in\events$.\end{definition}

For example, any cryptodeterministic QIVPM is $0$-deterministic.
For another example, given a three-dimensional Hilbert space, a $\frac{1}{3}$-deterministic
QIVPM can be given by $\bar{\mu}\left(P\right)=\left[x,x\right]$,
where $P$ projects onto a $x$-dimensional subspace. By utilizing
$\delta$-deterministic QIVPMs, we can have a Kochen-Specker theorem
with finite precision measurement.

@@

\begin{proof}Suppose there is a $\delta$-deterministic QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$,
then we can define a cryptodeterministic QIVPM\nb$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $
by 
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
\end{cases}
\end{equation}

The essential part to verify $\bar{\mu}^{\textrm{D}}$ is a cryptodeterministic
QIVPM is to verify a special case of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs\\
 & \Rightarrow & \bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs
\end{eqnarray}
\end{subequations}for orthogonal operators\nb$P_{0}$ and $P_{1}$.

@@

The remain part of the proof are routine verification.\end{proof}

>>>>

\begin{definition}\label{def:delta-deterministic}A QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
is called $\delta$-deterministic if either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$ for
any $P\in\events$.\end{definition}

For example, any cryptodeterministic QIVPM is $0$-deterministic.
As another example, a $\frac{1}{3}$-deterministic QIVPM can be given
by $\bar{\mu}\left(P\right)=\left[x/3,x/3\right]$, where $P$ projects
onto a $x$-dimensional subspace in a three-dimensional Hilbert space.
By utilizing $\delta$-deterministic QIVPMs, we can have a Kochen-Specker
theorem with finite precision measurement.

@@

\begin{proof}Suppose there is a $\delta$-deterministic QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$,
we can define a cryptodeterministic QIVPM\nb$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $
by 
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
\end{cases}
\end{equation}
However, there is no cryptodeterministic QIVPM as we discussed according
to the Mermin-Peres square, so that there is no $\delta$-deterministic
QIVPM.

The essential part to verify $\bar{\mu}^{\textrm{D}}$ is a cryptodeterministic
QIVPM is to verify a special case of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs\\
 & \Rightarrow & \bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs
\end{eqnarray}
\end{subequations}for orthogonal operators\nb$P_{0}$ and $P_{1}$.

@@

By discussing the remaining cases, we can easily verify that $\bar{\mu}^{\textrm{D}}$
is a cryptodeterministic QIVPM.\end{proof}
